Interleaved Serial and Decision-Theoretic Planning for a Mobile Robot

### 2011-01-20 subarchitectures/planner.sa/trunk/src/latex/IJCAI/ijcai11.tex
New title and abstract

\title{A Switching Planner for Combined Task and Observation Planning}
\author{anonymous}

@@

Realistic robot planning problems in uncertain environments often
require achieving tasks while also finding out about the
world. Because the world state cannot be observed directly, these
problems are naturally represented as partially observable Markov
decision problems (POMDPs). However, these are typically intractable
for realistic problems.
%%
We present a \emph{switching planner} that employs fast sequential
planning to decide on the overall strategy, and uses a
decision-theoretic planner to solve the subproblems where partial
observability will significantly impact the quality of the plan. We
demonstrate the approach in a realistic robot exploration domain.

>>>>

\title{Interleaved Serial and Decision-Theoretic Planning for a Mobile Robot}
%%\title{Interleaved Serial and Decision-Theoretic Planning for
%%Practical Robot Control}

%% \title{A Switching Planner for Combined Task and Observation Planning}
\author{anonymous}

@@

%% Those processes must

From an automated planning perspective the problem of practical mobile
robot control in realistic environments poses many important and
contrary challenges.  On the one hand, the planning process must be
lightweight, robust, and timely. Over the lifetime of the robot it
must always respond quickly with new plans that accommodate exogenous
events, changing objectives, and the underlying unpredictability of
the environment.  On the other hand, in order to exhibit useful
behaviours the planning process must perform computationally expensive
reasoning about contingencies and possible revisions of subjective
beliefs according to quantitatively modelled uncertainty in acting and
sensing.
%%
Addressing these challenges, we develop a \emph{continual planning}
approach that {\em switches} between using a fast satisficing
``classical'' planner, to decide on the overall strategy, and
decision-theoretic planning to solve small subproblems where deeper
consideration of the sensing model is practical, and can significantly
impact overall performance. We demonstrate our approach in a realistic
robot exploration domain.

%% partial observability

%% In cooperation with execution monitoring, it must perform repair
%% and/or replanning in order to seamlessly accommodate exogenous events,
%% changing objectives, and the underlying unpredictability of the
%% environment.

%% Realistic robot planning problems in uncertain environments often
%% require achieving tasks while also finding out about the
%% world. Because the world state cannot be observed directly, these
%% problems are naturally represented as partially observable Markov
%% decision problems (POMDPs). However, these are typically intractable
%% for realistic problems.
%%
